---
title: "R Notebook"
output: html_notebook
---
0.1 Needed Packages
```{r}
install.packages(c('readr', 'svDialogs', 'dplyr'))
library(readr)
library(svDialogs)
library(dplyr)
```

0.2 Load Data
```{r}
#Load 
spotify_top50 <- read.csv("https://gist.githubusercontent.com/rioto9858/ff72b72b3bf5754d29dd1ebf898fc893/raw/1164a139a780b0826faef36c865da65f2d3573e0/top50MusicFrom2010-2019.csv", header=TRUE, sep=",")

project = list()
project$data$spotify_top50 = list(
  value=spotify_top50,
  description="spotify_top50_from_2010_to_2019",
  source="https://gist.githubusercontent.com/rioto9858/ff72b72b3bf5754d29dd1ebf898fc893/raw/1164a139a780b0826faef36c865da65f2d3573e0/top50MusicFrom2010-2019.csv"
)
```

0.3 Have a look
```{r}
#how data looks like 
View(spotify_top50)
summary(spotify_top50)
```

0.4 Change column names for convenience
```{r}
#Change column names for convenience
colnames(spotify_top50) <- c('title','artist','genre','year', 'beats_per_min', 'energy', 'danceability', 'loudness', 'liveness', 'valence', 'length', 'acousticness', 'speechiness', 'popularity')
#Establish list of music genres
genres <- unique(spotify_top50$genre)
head(spotify_top50)
```

1. Collect user information
```{r}
user <- list()
user$name <- dlgInput("What's your name ?", Sys.info()["user"])$res
user$chosen_genres <- dlg_list(genres, multiple = TRUE, title = "Choose a genre that you like : ")$res

like_danceability <- dlgInput("Do you like danceable songs (T or F): ")$res
if(like_danceability == "T"){user$like_danceability <- TRUE} else if (like_danceability == "F"){user$like_danceability <- FALSE} else {user$like_danceability <- NA}

like_loudness <- dlgInput("Do you like loud songs (T or F): ")$res
if(like_loudness == "T"){user$like_loudness <- TRUE} else if (like_loudness == "F"){user$like_loudness <- FALSE} else {user$like_loudness <- NA}

like_energetic <- dlgInput("Do you like energetic songs (T or F): ")$res
if(like_energetic == "T"){user$like_energetic <- TRUE} else if (like_energetic == "F"){user$like_energetic <- FALSE} else {user$like_energetic <- NA}

user$created_playlists <- list()
print(user)
```

2. Song recommendation 
```{r}
filtered_by_genre <- filter(spotify_top50, genre == user$chosen_genres[[sample(1:length(user$chosen_genres),1)]])
#View(filtered_by_genre)

user$recommended_song <- filtered_by_genre[sample(1:length(unique(filtered_by_genre$title)), 1, replace=FALSE),]
paste0("You like the genre \'", user$recommended_song$genre, "\' then you'll like this song for sure : ", user$recommended_song$title, " - ", user$recommended_song$artist," (", user$recommended_song$year,")")
```
2.1 Let's play the song
```{r}
#Let's play the song ! (Spotify account needed)
#browseURL(paste("https://open.spotify.com/search/",gsub("[[:space:]]", "%", user.recommended_song$title),"%",gsub("[[:space:]]", "%", user.recommended_song$artist)))
user$recommended_song$url <- paste("https://www.youtube.com/results?search_query=",gsub("[[:space:]]", "+", user$recommended_song$title),gsub("[[:space:]]", "+", user$recommended_song$artist))
browseURL(user$recommended_song$url)
```

3. Create playlist with a song of each music genre -> "let's discover playlist"
```{r}
lets_discover_playlist = data.frame(matrix(ncol = 14, nrow = 0))
colnames(lets_discover_playlist) <- colnames(spotify_top50)
for(i in 1:length(genres)){
  filtered <- filter(spotify_top50, genre == genres[[i]])
  #(list_filtered[sample(1:length(unique(list_filtered$title)),1,replace=FALSE),]) #Debug
  lets_discover_playlist[nrow(lets_discover_playlist) + 1,] <- filtered[sample(1:length(unique(filtered$title)),1,replace=FALSE),] #Add into lets_discover_playlist
}

user$lets_discover_playlist <- lets_discover_playlist
if(dlgInput("See playlist details (T or F)")$res){
  View(user$lets_discover_playlist)
} else {
  View(select(user$lets_discover_playlist, title, artist, genre))
}
```

4. Create playlist with you favorite choices
```{r}
playlist <- list()
playlist$name <- dlgInput("Type the name of you new playlist : ")$res
playlist$duration <- strtoi(dlgInput("How long do you want it to last in minutes (recommended 60)")$res)
```

4.1 Create the playlist
```{r}
#user$created_playlists <- list() #Debug 
filtered <- filter(spotify_top50, genre == user$chosen_genres)
if(user$like_danceability){
  filtered <- filter(filtered, danceability >= mean(spotify_top50$danceability))
} else if (!user$like_danceability){
  filtered <- filter(filtered, danceability < mean(spotify_top50$danceability))
}
if(user$like_loudness){
  filtered <- filter(filtered, loudness >= mean(spotify_top50$loudness))
} else if (!user$like_loudness){
  filtered <- filter(filtered, loudness < mean(spotify_top50$loudness))
}
if(user$like_energetic){
  filtered <- filter(filtered, energy >= mean(spotify_top50$energy))
} else if (!user$like_danceability){
  filtered <- filter(filtered, energy < mean(spotify_top50$energy))
}

#adjust the length of the playlist
if(sum(spotify_top50$length)/60 < playlist$duration){
  paste0("Sorry we don't have enough songs to recommend the following playlist lasts ", sum(spotify_top50$length)/60, "min.")
  playlist$content <- filtered
  user$created_playlists[[length(user$created_playlists)+1]] <- playlist
} else {
  playlist$content <- filtered
  while(sum(playlist$content$length)-mean(spotify_top50$length)>=playlist$duration*60){
    playlist$content <- playlist$content[-c(sample(1:length(playlist$content$length), 1)),] #Remove random 
  }
  user$created_playlists[[length(user$created_playlists)+1]] <- playlist
}
#print(user$created_playlists[[1]])
View(user$created_playlists[[length(user$created_playlists)]]$content)
paste0("Your playlist '",user$created_playlists[[length(user$created_playlists)]]$name,"' (", sum(user$created_playlists[[length(user$created_playlists)]]$content$length)/60, "minutes) has been successfully created.")
```


#Wanna get famous, what genre works better (what is the genre that has more famous songs)


#What type of song regarding the genre (acousticness, loudness, ...)




----------------------------------------------------------------------------------------------------------------------------------------------------------------------------
#Selecting multiple 
```{r}
# Select one or several months
res <- dlg_list(month.name, multiple = TRUE)$res
if (!length(res)) {
  cat("You cancelled the choice\n")
} else {
  cat("You selected:\n")
  print(res)
}
```



user = list(
        name = "name", 
        chosen_genres = list("hip hop", "latin", "...", ...),
        like_danceability = True, 
        like_loudness = False, 
        recommended_song = df.row,
        lets_discover_playlist = df(50rows),
        created_playlists = list()
)









```{r}
text <- cbind(2, "salut")
cat(paste(text, collapse="."))
```

```{r}
library(svDialogs)
user.input <- dlgInput("Enter a number", Sys.info()["user"])$res
```

```{r}
#Create playlist
#What type of song should you do in order to get famous
my.name <- readline(prompt="Enter name: ")
my.age <- readline(prompt="Enter age: ")
# convert character into integer
my.age <- as.integer(my.age)
print(paste("Hi,", my.name, "next year you will be", my.age+1, "years old."))
```
