---
title: "110-1-r4ds Midterm"
params:
  name: "Mirko Rivas"
  id: "410979192"
editor_options: 
  chunk_output_type: console
---

**Please change John to your name, and 007 to your school id.**

The exam has two part:

# Part 1: Multiple choices (full mark = 72)

10 Questions. Each is worth 7 points. Please run the following command to visit the form for multiple choices.

Execute the following code chunk brings you to the MCQ form. Please complete MCQ there.

```{r}
browseURL("https://forms.gle/Z9gA9k5hCXW1wfck6")
```

# Part 2: Programming Question (Full mark is 30)

## Before you start

Each question is framed like:

*`Create an object named practice and bind a numeric value of 5 to it.`*

```{r ans0}
# practice
```

-   Put your program to solve the question inside the corresponding code chunk that has a label `ansXX` where `XX` is some number. (程式碼請寫在帶有`ansXX`標籤的code chunk裡)

-   Program should proceed the last `# yyyy` line where `yyyy` is some object name for this question. Here `# practice` is the last line. (Code chunk裡的程式碼必需插在最後一行`# yyyy` (這裡是`# practice`)的前面）

-   Never delete or modify the last line `# yyyy`. (千萬不能刪除或更動最後一行`# yyyy`的內容)

## The Question

# 1 Restaurant information （15 points)

Ti Jo Kitchen is located at "1F, No. 12-2, Daguan Rd, Sanxia District, New Taipei City, 237". It opens from Tuesday to Sunday, from 11:30AM to 8:30PM, but closes on Monday. Free Wi-Fi is available.

```{r}
ti_jo_kitchen$name # show "Ti Jo Kitchen"
ti_jo_kitchen$address # show
# "1F, No. 12-2, Daguan Rd, Sanxia District, New Taipei City, 237"
ti_jo_kitchen$`free-wifi` # show
# TRUE

names(ti_jo_kitchen$businessHours) # show
# c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")

ti_jo_kitchen$businessHours$XXXday # show 
# "11:30AM to 8:30PM" when XXXday is not Monday
# NA when XXXday is Monday
```

Construct `ti_jo_kitchen` object that can satisfy the above conditions:

```{r ans1}
ti_jo_kitchen = list(
  name = "Ti Jo Kitchen", 
  address = "1F, No. 12-2, Daguan Rd, Sanxia District, New Taipei City, 237", 
  `free-wifi`= TRUE, 
  businessHours = list(      
      "Monday" = NA, 
      "Tuesday" = "11:30AM to 8:30PM",
      "Wednesday" = "11:30AM to 8:30PM",
      "Thursday" = "11:30AM to 8:30PM", 
      "Friday" = "11:30AM to 8:30PM", 
      "Saturday" = "11:30AM to 8:30PM", 
      "Sunday" = "11:30AM to 8:30PM"
  ) 
)
ti_jo_kitchen
# ti_jo_kitchen
```

# 2 My day (10points)

At 9AM, I attend the class 'Accounting', which can be check via:

```{r}
Me$`9AM`$AttendClass$name
```

Lunch time at 12PM, I ate at Ti Jo Kitchen whose information is kept at

```{r}
Me$`12PM`$EatLunch$Restaurant # has the value as ti_jo_kitchen
```

Friends who accompany me for lunch are "John" and "Mary", which I kept at

```{r}
Me$`12PM`$EatLunch$companions
```

Construct `Me` object

```{r ans2}
Me = list(
  `9AM`= list(
    "AttendClass" = list(
      "name" = "Accounting"
    )
  ), 
  `12PM`= list(
    "EatLunch" = list(
      "Restaurant" = ti_jo_kitchen, 
      "companions" = list("John", "Mary")
    )
    
  )
)
Me$`9AM`$AttendClass$name
Me$`12PM`$EatLunch$Restaurant # has the value as ti_jo_kitchen
Me$`12PM`$EatLunch$companions
Me
#Me
```

# 3 My mistake (5 points)

In the previous journal, I made a mistake. I attended the class at 10AM instead of 9AM. Please help me correct that:

```{r ans3}
names(Me)[[1]] <- "10AM"
# Me
```
