---
title: "R Notebook"
output: html_notebook
---

Insérer une code chunk *Ctrl+Alt+I*

```{r}
#Différence entre plot et print
plot(cars)
print(cars)
```


Chapter 2 
2.4 Data (Atomic)
```{r}
"String" #"Mary", "EJHFä1341"
Numeric #2L (Integer), 2(Integer), 2.4(Double), 
Logical #TRUE, FALSE
```

2.5 Collections
```{r}
#Atomic Vector contains only the same type of value
c("John", "Mary")
c(2, 3.1412)
c(TRUE, TRUE, F)
typeof(c(TRUE, TRUE, F)) #Determiné par le type des données(logical)

#List (general vector) contains different types of values
list("John", 178, TRUE)
typeof(list("John", 178, TRUE))
```

2.6 Values and element Values
```{r}
#A single basic type value, a vector or a list can represent a value!
"John"
12
c(2, 3.1412)
list("John", 178, TRUE)

#Element value is an element inside of a vector or a list 
list("John", 5, TRUE) # has 3 element values.
list("John",42, list("Mary", 35)) # has also 3 element values.! "Mary" is not a element value of the big list, since it is in a smaller inside another vector 
```

2.7 Retrieve ONE element value by position
```{r}
#Double brackets [[]]
c("John", "Mary")[[1]]
c("John", "Mary")[[2]]

#Retrieve 35
bigList <- list("John",42, list("Mary", 35))
bigList[[3]][[2]]

#!!2 vectors make 1
vector <- c(c("mary", "John"), c(1,2))
vector[[3]][[1]] #!!! Pareil pour un vecteur qui contient des listes!

vector2 <- list(c("mary", "John"), c(1,2))
vector2[[2]][[1]] #Retrieve 1
```

2.8 Binding (assign a name with a value)
```{r}
#Difference between Binding and Name call
personName1 = c("John", "Mary")
personName2 <- c("John", "Mary")
c("John", "Mary") -> personName3

personName4 = list("John", "Mary")
personName5 <- list("John", "Mary")
list("John", "Mary") -> personName6

personName1[[2]]
personName4[[2]]

#Name calls
element1 <- "a"
element2 <- "b"
c(element1, element2) # there are two name calls
```

Some valid names for Binding
```{r}
my_108_total_credits <- 15
my.108.total_credits <- 15
.my.108.total_credits <- 15 #start with . will hide name
`.108.total_credits` <- 15 #irregular name, ` is not part of the name
`108 total credits` <- 15
```

2.9 Concatenate
```{r}
#Concatenate atomic vectors
typeof(c("a", "b"))
typeof(c("c", "d"))
c(c("a", "b"), c("c", "d")) 

#Concatenate des listes à l'aide d'un vecteur
liste = c(list("a", 1), list("c", 2))
liste[[4]]
liste

#Concatenate le paste
paste0("salut", "jean")
paste("salut", "jean")
```

2.10 List
```{r}
list(c("a", "b"), c("c", "d")) # (1)
# so (1) is not the same as
list("a", "b", "c", "d")

#These two are not the same too
c(c("a", "b"), c("c", "d"))[[1]]
list(c("a", "b"), c("c", "d"))[[1]] # Error

#Coercion
coercion <- c(c("a", "b"), c(1, 22))
typeof(coercion[[3]])
#coercion[[3]] + 2 #Error 

#With others than character
coercion2 <- c(c(1,2), c(TRUE, FALSE))
coercion2
coercion3 <- c(c(TRUE, FALSE), c(1,2))
coercion3
```

2.11 Sampled data (Observation by observation)
```{r}
#age, gender, residential district, etc
list(54, "male", "north", 100) # (1)
list(32, "female", "south", 25) # (2)
list(28, "female", "east", NA) # (3) NA -> If value not assigned 
list(20, "male", "east", 77) # (4)

#Put all together
oByO1 <- list(
  list(54, "male", "north", 100), # (1)
  list(32, "female", "south", 25), # (2)
  list(28, "female", "east", NA), # (3)
  list(20, "male", "east", 77) # (4)
)

#Why not in an atomic vector? 
oByO2 <- c(
  list(54, "male", "north", 100), # (1)
  list(32, "female", "south", 25), # (2)
  list(28, "female", "east", NA), # (3)
  list(20, "male", "east", 77) # (4)
)
persons2 #Met tout sur un même et seul niveau (comme une big liste qui contient toutes les valeurs à la suite)
```

2.11 (Feature by feature)
```{r}
#Put all together
fByF <- list(
  c(54, 32, 28, 20), # age
  c("male", "female", "female", "male"), # gender
  c("north", "south", "east", "east"), # residence
  c(100, 25, NA, 77) # income  
)

#Why not in an atomic vector? 
fByF2 <- c(
  c(54, 32, 28, 20), # age
  c("male", "female", "female", "male"), # gender
  c("north", "south", "east", "east"), # residence
  c(100, 25, NA, 77) # income  
)
fByF2 #Met tout sur un même et seul niveau (comme une big liste qui contient toutes les valeurs à la suite)
```

2.12 Named element values
```{r}
# atomic vector
c("John"=177, "Mary"=160, "Bill"=170)
# list
list("John"=177, "Mary"=160, "Bill"=170)

#With irregular name
list(
  "1st Observation"=list(54, "male", "north", 100), 
  "2nd Observation"=list(32, "female", "south", 25), 
  "3rd Observation"=list(28, "female", "east", NA), 
  "4th Observation"=list(20, "male", "east", 77) 
)

#With regular name
personInfo = list(
  firstObservation=list(54, "male", "north", 100), 
  secondObservation=list(32, "female", "south", 25)
  )

#Retrieve values 
personInfo[[2]]
personInfo[["firstObservation"]]
personInfo[["secondObservation"]][[1]]
```

2.13 Retrieve element value by element name
```{r}
sample_data <- 
  list(
    "1st Observation"=list(54, "male", "north", 100), 
    "2nd Observation"=list(32, "female", "south", 25), 
    "3rd Observation"=list(28, "female", "east", NA), 
    "4th Observation"=list(20, "male", "east", 77)
  )
sample_data[["4th Observation"]]

#Vector
a <- c(1, 3, elementName=7)
a[[1]]
a[["elementName"]]
#a[[elementName]] #Not work 
#a[[`elementName`]] #Not Work

#This works because because targetName is "elementName"
targetName <- "elementName"
a[[targetName]]
```

2.14 list only $ extractor
```{r}
sample_data <- list(
  "observation1"=list(54, "male", "north", 100), 
  "observation2"=list(32, "female", "south", 25), 
  "observation3"=list(28, "female", "east", NA), 
  "observation4"=list(20, "male", "east", 77)
)
sample_data[["observation4"]][[1]]
sample_data$"observation4"[[1]]
sample_data$`observation4`[[1]]
sample_data$observation4[[1]]
```

Chapter 3
3.1 Element values
```{r}
#Labelled vs non-labelled items
nLbld = list(
  "milk", 
  "apple", 
  "pork"
)
lbld = list(
  Compulsory = 
    c("Principle of Economics", "Calculus", "Accounting"),
  Selective = 
    c("Philosophy","Chinese Literature")
)
lbld$Selective

#Nested list
list(
  name="Gianandrea Noseda conducts Schumann and Mendelssohn — With Mikhail Pletnev",
  time="2021, Oct, 01",
  program=list(
    "Robert Schumann, Piano Concerto in A Minor, Op. 54",
    "Felix Mendelssohn-Bartholdy, Symphony No. 4 in A Major, Op. 90, Italian"
  )
)
```

3.2 JSON Data
```{r}
# Observation by observation
concerts_obo <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = F)

# Feature by feature
concerts_fbf <-
  jsonlite::fromJSON("https://cloud.culture.tw/frontsite/trans/SearchShowAction.do?method=doFindTypeJ&category=17", simplifyDataFrame = T)

concerts_obo[[1]]
View(concerts_fbf) #It's a dataframe
```

3.2 Retrieve multiple element values
```{r}
JohnsFamily <-
  list(
    name = "John", 
    age = 35,
    spouse = list(name = "Mary", age = 32),
    children = list(
                  list(name = "Bill", age = 5),
                  list(name = "Jane", age = 3)
                )
  ) #This list has 4 elements, element names are "name, age, spouse and children"

length(JohnsFamily)
names(JohnsFamily)

#Sys.Date() gives the system's date
Sys.Date()

#Johns name and age !! Only 1 [], if juste one retrieval then double [[]]
JohnsFamily[c(1,2)]
JohnsFamily[c("name", "age")]
```

3.3 Value replacement 
```{r}
# [[]]<-, []<-, $ <-
#replace 1 value
johnsFamilyCopy <- JohnsFamily
johnsFamilyCopy[[1]] = "Watson"
johnsFamilyCopy[["age"]] <- 11
"Lennon" -> johnsFamilyCopy$children[[1]]$name

#Replace multiple values
johnsFamilyCopy2 <- JohnsFamily
johnsFamilyCopy2[c(1,2)] <- list("name"="Watson2", "age"=22)
johnsFamilyCopy2[c(1,2)] <- list("Watson2", 22) #The same as above
johnsFamilyCopy2[c(2)] <- 25

johnsFamilyCopy
johnsFamilyCopy2
```


3.4.1 Add element values
```{r}
example1 <- c("John", "Mary", "Bill")

#add following index (retrieve an non-existing element name "person4")
example1[["person4"]] <- "Ken"
#Add index 7 and 8 (retrieve two non-existing element positions)
example1[c(7,8)] <- c("person7"="Jack", "Janem")
example1

#with $
johnsFamilyCopy3 <- JohnsFamily
johnsFamilyCopy3$children[[3]] <- 
  "John" # False because not following the same structure($ is for list only)
johnsFamilyCopy3$children[[3]] <- list(name="Lisa", age=0) #This one's right
johnsFamilyCopy3

```

3.4.2 Data Construction
```{r}
#Two types of construction
height <- c("001"=177, "002"=183, "003"=173)
height2 <- numeric(0) # Declaration
height2[["001"]] <- 177
height2[c("002", "003")] <- c(183, 173)

#Another example with length 3, (can be logical(0) or list())
chars = character(3)
chars
```

3.4.3 Data construction
```{r}
# Suppose this query Retrieve the 1st course in semester 1, school year 108
#classSchedule$yr108$semester1[[1]] 
#create the structure
classSchedule <- list()
classSchedule[["yr108"]] <- list("semester1"=list("Programming", "SQL", "Machine Learning"), semester2=list("Data Mining", "Java", "OOP"))
classSchedule$yr108$semester1[[1]] 
classSchedule

#Simpler way
classSchedule2 <- list()
classSchedule2$yr108$semester1$course1$name <- "Programming"
classSchedule2$yr108$semester1$course1[["credit"]] <- 2
classSchedule2
```

3.5 Remove element values
```{r}
example2 <- c("John", "Mary", "Bill", person4="Jack")

#Remove jack 
example2 <- example2[c(1, 2, 3)]
```
    #Sequences
    1:3 # from 1 to 3, each increases by 1
    7:11
    2:-1 # from 2 to -1, each decreases by 1
```{r}
example2[c(1,2,3)] # the same as
example2[1:3]

#Sequence
seq(from=1, to=3, by=1) # from 1 to 3 increase by 1
seq(from=3, to=11, by=4) # from 3 to 11 increase by 4
seq(from=3, to=11, length.out=10) # divide interval [3, 11] into 10 equal length cuts

#Inclusive, exclusive, multiple exclusion and exclusive indexation
example3 <- c("John", "Mary", "Bill", person4="Jack")

## inclusive approach
example3[c(1, 2, 3)]

## exclusive approach
example3[-c(4)]

## multiple exclusion is possible
example3[-c(1, 4)]


##Exclusive indexation
example4 <- c("John", "Mary", "Bill", person4="Jack")
# Object source <- retrieval of elements to keep
example4 <-
  example4[-c(4)] #!! Does not work with element name instead of index
```

Another example
```{r}
example5 <- c("John", "Mary", "Bill", person4="Jack")
## exclude 2 to 4
example5[-c(2, 3, 4)]

example6 <- c("John", "Mary", "Bill", person4="Jack")
## exclude 2 to 4
example6[-c(2:4)]
```

Bind with NULL or retrieval
```{r}
johnsFamilyCopy4 <- JohnsFamily

#bind with NULL
johnsFamilyCopy4$spouse <- NULL

#bind the lists with null
johnsFamilyCopy4[c(3, 4)] <- NULL

johnsFamilyCopy4
```

3.6 Example on data Taipei
```{r}
mrtStationAds <- 
  httr::content(httr::GET("https://data.taipei/api/v1/dataset/91290609-2b8b-4130-8ce9-e6085529bc46?scope=resourceAquire&limit=1000"))
mrtStationAds

maokongGondola <- httr::content(httr::GET("https://ptx.transportdata.tw/MOTC/v2/Rail/Metro/Station/TRTC?$top=30&$format=JSON"))
maokongGondola
```

TESTS
```{r}
persons <- c(dad <- "john", mom = "mary")
persons2 <- c(dad="john", mom = "mary")

persons[c(2)] <- 4
persons
persons2

liste <- list(a <- 3, b <- 4)
a
b

list(3, 4, 5)[c(3)]

x <- numeric(0)
x <- c(12, "chloe", TRUE)
typeof(x)
```




